\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Spatiotemporal modeling of \emph{Mtb} transmission in a South African primary care clinic}

### 2023-07-18 doc/paper/supplements.tex
Updates from Overleaf

The diffusion constant $D$ is unknown but can be approximated using an empirical relationship between the eddy diffusion coefficient $K$ and the outdoor air exchange rate $AER$ (in air changes/h)
\begin{align}
    K = (0.52 \cdot AER + 8.61e-5) * V^(2/3),
\end{align}
where $V$ is the volume of the airspace (in m$^3$). We assume that $D \approx K$.

@@

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Quanta concentration at different time points following the generation of the first quanta (8:00:00am) and last quanta (9:00:00am) from an infectious individual that is placed in a fixed location in the middle of the room with dimensions L=10$\times$B=\5$\times$H=3m.}
    \label{fig:toy-example}
\end{figure}

>>>>

The diffusion constant $D$ is unknown but can be approximated using an empirical relationship between the eddy diffusion coefficient $K$ and the outdoor air exchange rate $AER$ (in air changes/h)
\begin{align}
    K = (0.52 \cdot AER + 8.61e-5) * V^{\frac{2}{3}},
\end{align}
where $V$ is the volume of the airspace (in m$^3$). We assume that $D \approx K$.

@@

\begin{figure}
    \centering
    \includegraphics{../../tests/stm_v2-toy_example.pdf}
    \caption{Quanta concentration at different time points following the generation of the first quanta (8:00:00am) and last quanta (9:00:00am) from an infectious individual that is placed in a fixed location in the middle of the room with dimensions L=10m$\times$B=5m$\times$H=3m.}
    \label{fig:toy-example}
\end{figure}
